% !TEX program = xelatex

\documentclass[11pt]{article}
\usepackage[
    a4paper,
    left=0.8in,
    right=0.8in,
    top=1in,
    bottom=1in,
    footskip=.25in
]{geometry}

% A Few Useful Packages
\usepackage{marvosym}
\usepackage{fontspec} %for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} % other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{supertabular} % for Grades
\usepackage{longtable} % for tables
\usepackage{titlesec} % custom "\section"
\usepackage{color} % for text colors

% Setup hyperref package, and colors for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

% Setup Fonts with "fontspec" package
\defaultfontfeatures{Mapping=tex-text}
\setmainfont[
    Path = fonts/,
    SmallCapsFont = Fontin-SmallCaps.otf,
    BoldFont = Fontin-Bold.otf,
    ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}

% Setup title styles
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}

% Italian hyphenation for the word: ''corporations''
\hyphenation{im-pre-se}

%-------------------------------------------------------------
%----------------------- BEGIN DOCUMENT ----------------------
%-------------------------------------------------------------

\begin{document}

% non-numbered pages
%\pagestyle{empty} 

% for use with \LaTeX command
\font\fb=''[cmr10]'' 

% ----------------------- Header -----------------------
\par{\centering{\Huge \textsc{Nikolaos Anyfantis}}\par}
\par{\centering{\textsc{Curriculum Vitae}}\par}
% \par{\centering{\textsc{\textcolor{red}{Last Update: December 2020}}}\par}
\bigskip

% ----------------------- Personal Data -----------------------
\section{Personal Data}

\begin{tabular}{rl}
    \textsc{Place \& Date of Birth:}    & Heraklion, Greece | 08 Sept 1989 \\
    \textsc{Address:}                   & 6 Laodamantos St., Heraklion - Crete, Greece \\
    \textsc{Telephone No. :}            & +30 697 3756607 \\
    \textsc{email:}                     & \href{mailto:nikosanif@gmail.com}{nikosanif@gmail.com} \\
    \textsc{Nationality:}               & Greek \\
\end{tabular}

% ----------------------- About me -----------------------
\section{About me}

\footnotesize{
    \begin{itemize}
        \item I'm currently working on Angular \& Node.js Application Development.
        \item Exploring new technologies and developing software solutions.
        \item I have studied Computer Science and Computer Programming.
        \item I work as a Lead Frontend Developer.
        \item I write articles at 
            \href{https://dev.to/nikosanif}{dev.to/nikosanif},
            \href{https://nikosanif.medium.com/}{nikosanif.medium.com},
            and contribute to Open Source at \href{https://devlibrary.withgoogle.com/authors/nikosanif}{Google Dev Lib}.
        \item Enthusiast in Angular and Web Technologies in general.
        \item I have a passion for sleek user-friendly design and I love writing nicely architectured, clean and maintainable code.
        \item How to reach me: 
            \href{https://github.com/nikosanif}{GitHub},
            \href{https://www.linkedin.com/in/nikosanifantis/}{LinkedIn},
            \href{https://twitter.com/nikosanif}{Twitter}.
    \end{itemize}
}


% ----------------------- Work Experience -----------------------
\section{Work Experience}

\begin{longtable}{r|p{12.5cm}}

% Turintech
\textsc{Jan 2021 – Present} & \textbf{Lead Frontend Developer} \\
\footnotesize{\textit{London, UK}} & \textsc{Turintech } \\
& \footnotesize{\textit{As a Lead Frontend Developer, I am responsible for overseeing the development and implementation of web applications. My role involves developing high-quality, scalable, and maintainable code, as well as mentoring and coaching junior frontend developers. I am also responsible for staying up-to-date with the latest industry trends and technologies, ensuring that the team is delivering innovative solutions to meet the needs of the business and its customers.}} \\

% HCI - FORTH
\multicolumn{2}{c}{} \\
\textsc{Apr 2016 – Jan 2021} & \textbf{Research \& Development Engineer} \\
\footnotesize{\textit{Heraklion, Greece}} & \textsc{Human Computer Interaction Laboratory (HCI) - ICS } \\
& \textsc{Foundation for Research and Technology (FORTH)} \\
& \footnotesize{\textit{RnD Engineer on both research and production project areas. Strong experience on intelligent environments with the use of artificial intelligent, sensor networks and pervasive and mobile computing. Moreover, experienced in design and development of significant production projects of remarkable companies.}} \\

% ISL - FORTH
\multicolumn{2}{c}{} \\
\textsc{Aug 2014 – Feb 2016} & \textbf{Software Developer, Research Assistant} \\
\footnotesize{\textit{Heraklion, Greece}} & \textsc{Information Systems Laboratory (ISL) - ICS } \\
& \textsc{Foundation for Research and Technology (FORTH)} \\
& \footnotesize{\textit{As a Research Assistant of Information Systems Laboratory team under supervision of professor Yannis Tzitzikas. Working on services of modern Intelligent Systems and Virtualization technologies on Semantic Web area.}} \\

% Public
% \multicolumn{2}{c}{} \\
% \textsc{Oct 2013 – Jul 2014} & \textbf{Sales Executive of IT Department} \\
% \footnotesize{\textit{Heraklion, Greece}} &\emph{\textsc{Public, Retail World A.E.}} \\

% CGSoft
\multicolumn{2}{c}{} \\
\textsc{Jun 2011 - Nov 2011} & \textbf{Software Developer} \\
\footnotesize{\textit{Athens, Greece}} & \emph{\textsc{CGSoft Company}} \\
& \footnotesize{\textit{Working as an undergraduate student on websites development based on Content Management Systems (CMS), such us Wordpress, Joomla and Magento.}} \\

\end{longtable}

% ----------------------- Education -----------------------
\section{Education}

\begin{longtable}{r|p{12.5cm}}

% MSc - UOC
\textsc{Feb 2014 - Feb 2016} & \textbf{University of Crete} \\
\footnotesize{\textit{Heraklion, Greece}} & \textsc{M.Sc.} in \textsc{Computer Science} - \textsc{Gpa}: 9/10\\
& Specialization: \textsc{Information Systems, Semantic Web, E-Commerce} \\
& Thesis: ``Mappings Management for Ontology-based Integration'' \\
& \footnotesize \small Advisor: Prof. Yannis \textsc{Tzitzikas}\\
& \footnotesize{Courses: 
    \textit{Semantic Web Data Management, Process Management Systems, 
    Advanced Topics in Human-Computer Interaction, Interactive Computer Graphics,
    Special Topics on E-commerce, Knowledge Representation and Reasoning}} \\

% BSc - PaPei
\multicolumn{2}{c}{} \\
\textsc{Sep 2007 – Sep 2011} & \textbf{University Of Piraeus} \\
\footnotesize{\textit{Piraeus, Greece}} & \textsc{B.Sc.} in \textsc{Informatics} - \textsc{Gpa}: 7.8/10 \\
& Specialization: \textsc{Information Systems} \\
& Thesis: ``IT Systems Security and Penetration Testing'' \\
& \footnotesize \small Advisor: Prof. Euaggelos \textsc{Fountas} \\
& \footnotesize{Important Courses: 
    \textit{Data Structures, Algorithms, Internet and
    Web Programming, Software Engineering, Data Warehousing
    and Data Mining, Information Retrieval and Searching on the
    World Wide Web, Internet-Based Information Systems}} \\

\end{longtable}

% ----------------------- Technical Skills -----------------------
\section{Technical Skills}

\begin{longtable}{rp{12cm}}

\textbf{Frond-End Programming} 
& Angular, Typescript, JavaScript, NgRX, RxJS, Angular Material \\
& Fetch API / Ajax, Web Sockets, Server-sent Events, HTML5, CSS3 (SASS, LESS), Material Design, Bootstrap, D3js \\

\multicolumn{2}{c}{} \\
\textbf{Back-End Programming} 
& Node.js, NestJS, Express.js, Fastify, Mongoose, MikroORM, Java, C\#, JWT Auth, REST/SOAP API Services, Shell scripting \\

\multicolumn{2}{c}{} \\
\textbf{DBM Systems} 
& NoSQL - MongoDB, ElasticSearch, Neo4J, RDF/S, SparQL \\
& SQL - PostgreSQL, MySQL, Oracle  \\

\multicolumn{2}{c}{} \\
\textbf{Message Brokers} 
& Apache Kafka, Redis, RabbitMQ \\

\multicolumn{2}{c}{} \\
\textbf{DevOps} 
& Docker, Docker Compose, GitHub Actions, GitLab CI/CD \\

\multicolumn{2}{c}{} \\
\textbf{Development Tools} 
& NPM, Yarn, NX monorepos, Prettier, ESLint, esbuild, Webpack, Conventional commits, Swagger \\

\multicolumn{2}{c}{} \\
\textbf{Version Control Systems} 
& GIT (GitHub, GitLab, Bitbucket, TortoiseGIT), SVN \\

\multicolumn{2}{c}{} \\
\textbf{Data Formats} 
& JSON, YAML, XML, Xpath, Xquery, XSLT, XSD \\

\multicolumn{2}{c}{} \\
\textbf{Software Platforms} 
& VSCode, WebStorm, Visual Studio, Adobe Photoshop, Adobe XD, Microsoft Office Suite, \LaTeX \\

\multicolumn{2}{c}{} \\
\textbf{Other skills} 
& - Extensive hands-on experience with Angular and NestJS (Node.js) \\
& - Lead projects and supervise a small team \\
& - Strong attention to detail and good problem-solving \\
& - Staying up-to-date with the latest industry trends and technologies \\
& - Good verbal and written communication skills \\

% \multicolumn{2}{c}{} \\
% \textbf{Modelling} 
% & UML, Venn \\

% \multicolumn{2}{c}{} \\
% \textbf{Semantic web \& Ontologies} 
% & Protégé, SPARQL, OWL, RDF/s \\

\end{longtable}

% ----------------------- Teaching Experience -----------------------
\section{Teaching Experience}

\begin{longtable}{r|p{12.5cm}}

\textsc{Winter Semester} & \textbf{CS100 - Introduction to Computer Science (C)}  \\
\textsc{2015-16 \& 2013-14} &\textsc{Teaching Assistant} at CS Dept. - University of Crete \\

\multicolumn{2}{c}{} \\
\textsc{Summer Semester} & \textbf{CS359 - Web Programming (Java, Servlets, JSP)}  \\
\textsc{2014-15} &\textsc{Teaching Assistant} at CS Dept. - University of Crete\\

\multicolumn{2}{c}{} \\
\textsc{Winter Semester} & \textbf{CS252 - Object-Oriented Programming (Java)}  \\
\textsc{2014-15} &\textsc{Teaching Assistant} at CS Dept. - University of Crete\\

\multicolumn{2}{c}{} \\
\textsc{Summer Semester} & \textbf{CS150 - Programming (C++)}  \\
\textsc{2013-14} &\textsc{Teaching Assistant} at CS Dept. - University of Crete\\

\end{longtable}

% ----------------------- Publications -----------------------
\section{Publications}

\begin{itemize}

\item 
\textbf{Paper}. 
Nikolaos Anyfantis, Evangelos Kalligiannakis, Achilleas Tsiolkas, Asterios Leonidis, Maria Korozi, Prodromos Lilitsis, Margherita Antona and Constantine Stephanidis "\textit{AmITV: Enhancing the Role of TV in Ambient Intelligence Environments}". Proceedings of the 11th PErvasive Technologies Related to Assistive Environments Conference. ACM, 2018. Corfu, Greece.

\item 
\textbf{Poster}.
Asterios Leonidis, Dimitrios Arampatzis, Nikolaos Louloudakis, Nikolaos Anyfantis, Achilleas Tsiolkas and Constantine Stephanidis. "\textit{AmI Solertis: a Web-IDE for Defining the Behaviour of Smart Environments}". 11th Scientific Conference of FORTH. October 13-14, 2017, Heraklion, Crete, Greece.

\item 
\textbf{Contribution in the context of MSc Thesis}. 
Yannis Marketakis, Nikos Minadakis, Haridimos Kondylakis, Konstantina Konsolaki, Georgios Samaritakis, Maria Theodoridou, Giorgos Flouris, Martin Doerr. "\textit{X3ML Mapping Framework for Information Integration in Cultural Heritage and beyond}". International Journal on Digital Libraries (2016).

\end{itemize}

% ----------------------- Certificates and Volunteerism -----------------------
\section{Certificates \& Volunteerism}

\begin{itemize}

\item
\textit{Technical host at HCI International 2020 Conference.} \\
July 19-24, 2020, FORTH-ICS, Heraklion, Crete, Greece.

\item
\textit{9th Symposium and Summer School on Service Oriented Computing - SummerSOC'15.} \\
June 2015, Crete, Greece.

\item
\textit{3rd MUMIA Training School on Information Retrieval.} \\
July 21-25, 2014, FORTH-ICS, Heraklion, Crete, Greece.

\item
\textit{Google Developer Groups - DevFest Crete 2015. Local ambassador.} \\
November 26-28, Heraklion, Crete, Greece.

\end{itemize}

% ----------------------- Notable Projects -----------------------
\section{Notable Projects}

\textsc{European Projects}
\begin{itemize}
\item
\textbf{InCulture} Collection, narrative correlation and presentation of the intangible cultural heritage. \\
\url{http://www.inculture-project.gr/}
\item
\textbf{CuRe} Cultures and Remembrances; Virtual time travels to the encounters of people from the 13th to 20th centuries. \\ 
\url{http://www.cure-project.gr/}
\item
\textbf{TranSOL} Transnational solidarity at time of crisis. The EC project TransSOL (WP 2). \\
\url{http://transsol.eu/project/}
\item
\textbf{LIVEWHAT} Living With Hard Times. The EC project LIVEWHAT (WP 6).  \\
\url{http://www.livewhat.unige.ch/}
\item
\textbf{BlueBRIDGE} is an EC funded project under the H2020 framework that kicked-off on 1st Sep 2015 aiming to further develop and exploit the iMarine e-Infrastructure data services for an ecosystem approach to fisheries. \\
\url{http://www.bluebridge-vres.eu/}
\end{itemize}

\textsc{Production Projects}
\begin{itemize}
\item
\textbf{Piraeus Bank.} Design and development of multimedia content presentation software and interactive in-store navigation (e-branch).
\item
\textbf{Bus Services.} Participation in the redesign of the information signs of arrivals and departures of the KTEL Heraklion - Lassithi, in the context of the development of interactive Diffuse Intelligence systems for the new intercity bus station.
\end{itemize}

\textsc{Research Projects}
\begin{itemize}
\item
\textbf{Intelligent House.} Design and orchestrate sophisticated mechanisms in order to enhance the everyday user activities with the use of pervasive and mobile computing, sensor networks, artificial intelligence, multimedia computing, middleware and agent-based software.
\item
\textbf{MatWare} is a tool for constructing domain-specific warehouses by aggregating semantic data. The main objective is to tackle the need for having integrated sets of facts regarding a particular domain. \url{http://www.ics.forth.gr/isl/MatWare/}
\end{itemize}

% \textsc{Academic Projects}
% \begin{itemize}
% \item
% Maven web application project that was implemented in the context of MSc thesis at the University of Crete. Keywords: Java, Javascript, JQuery, REST-services, JSON, Bootstrap, D3js, Treejs, Sigmajs. GitHub repository: \url{https://github.com/nikosanif/Maze}
% \item
% Web-based tool that offers exploration capabilities in linked data. Keywords: Java, JSP, Servlets, HTML5, CSS, Javascript, Semantic Web.
% \item
% Native application that provides a unified environment that employs a suite of interactive applications for supporting the users of a Smart Home. Keywords: C\#, WPF, Sql Server
% \item
% Web-based application that implements Score 4 game in the context of Knowledge Representation and Reasoning. Keywords: ASP, Prolog, Clingo, Java, Javascript, Ajax, JQuery, HTML5, CSS3, Ajax, JQuery
% \item
% Google App Engine applications. The purpose of this assignment was to be familiarized with the Google App Engine and some of its services. JSON (GSON), Java, JAX-RS, Google App Engine, REST-Services, SOAP Services
% \item
% Web Technologies - Creation of virtual enterprise Business Plan, SWOT Analysis, Website (Joomla)
% \item
% Implementation of Digital Library. Keywords: C\#, SQL, SQL Server
% \end{itemize}

% ----------------------- Additional Information -----------------------
\section{Additional Information}

\begin{tabular}{rl}
    \textsc{Languages:} 
    & Greek (native) \\
    & English - Professional working proficiency - Fluent \\
    & Spanish - Elementary proficiency \\

    \textsc{Driving License:} 
    & A, B \\
    
    \textsc{Military service:} 
    & 9 months military service (obligatory in Greece) \\ 
    & 24 November 2011 - 24 August 2012\\
    
    \textsc{Interests \& Activities:} 
    & Technology, Open-Source, Programming, Cinema, Music, Travelling \\

    \textsc{Reference Letters:} 
    & Available on request
\end{tabular}

\end{document}
